Synthesizing Symmetric Lenses

### 2018-07-05 papers/SymmetricLenses/main.tex
Fixed a sign
add in typo fix

\begin{theorem}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \item $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \end{enumerate}
\end{theorem}

@@

\begin{theorem*}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \item $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \end{enumerate}
\end{theorem*}
\begin{proof}
Given $s \in S$, let $V_{\ell}(s) = \{t \in \mathcal{L}(T) \; | \; \ell.\PutROf{s}{t} = t\}$. We want to show that
$$\sum_{s \in \mathcal{L}(S)}P_{\mathcal{L}(S)}(s)H(V_{\ell}(s)) = \mathbb{H}^{\rightarrow}(S \; | \; \ell, T)$$
We proceed by induction over $\ell$. 
\begin{enumerate}
\item
($\ell = \IdentityLensOf{S}$)

@@

&= \log_2 q * P_{T_1}(V_{\ell_1}(s)) + \log_2 P_{T_1}(V_{\ell_1}(s)) * P_{T_1}(V_{\ell_1}(s)) + P_{T_1}(V_{\ell_1}(s))*H(V_{\ell_1}(s))\\
&= P_{T_1}(V_{\ell_1}(s))[\log_2 q + \log_2 P_{T_1}(V_{\ell_1}(s)) + H(V_{\ell_1}(s))]

@@

&= \frac{q * P_{T_1}(V_{\ell_1}(s))[\log_2 q + \log_2 P_{T_1}(V_{\ell_1}(s)) + H(V_{\ell_1}(s))]}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\

@@

&= \frac{q * P_{T_1}(V_{\ell_1}(s)) \left[\log_2 q + \log_2 \left[\frac{P_{T_1}(V_{\ell_1}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] + H(V_{\ell_1}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}

@@

&= \frac{(1-q) * P_{T_2}(V_{\ell_2}(s)) \left[\log_2 (1-q) + \log_2 \left[\frac{P_{T_2}(V_{\ell_2}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] + H(V_{\ell_2}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}

@@

&= \frac{q * P_{T_1}(V_{\ell_1}(s)) \left[\log_2 q + \log_2 \left[\frac{P_{T_1}(V_{\ell_1}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] + H(V_{\ell_1}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&+ \frac{(1-q) * P_{T_2}(V_{\ell_2}(s)) \left[\log_2 (1-q) + \log_2 \left[\frac{P_{T_2}(V_{\ell_2}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] + H(V_{\ell_2}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}

>>>>

\begin{theorem}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \item $\LEntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \end{enumerate}
\end{theorem}

@@

\begin{theorem*}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \item $\LEntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \end{enumerate}
\end{theorem*}
\begin{proof}
Given $s \in S$, let $V_{\ell}(s) = \{t \in \mathcal{L}(T) \; | \; \ell.\PutROf{s}{t} = t\}$. We want to show that
$$\sum_{s \in \mathcal{L}(S)}P_{\mathcal{L}(S)}(s)H(V_{\ell}(s)) = \mathbb{H}^{\rightarrow}(S \; | \; \ell, T)$$
We proceed by induction over $\ell$. 
\begin{enumerate}
\item
($\ell = \IdentityLensOf{S}$)

@@

&= \log_2 q * P_{T_1}(V_{\ell_1}(s)) + \log_2 P_{T_1}(V_{\ell_1}(s)) * P_{T_1}(V_{\ell_1}(s)) + P_{T_1}(V_{\ell_1}(s))* -H(V_{\ell_1}(s))\\
&= P_{T_1}(V_{\ell_1}(s))[\log_2 q + \log_2 P_{T_1}(V_{\ell_1}(s)) - H(V_{\ell_1}(s))]

@@

&= \frac{q * P_{T_1}(V_{\ell_1}(s))[\log_2 q + \log_2 P_{T_1}(V_{\ell_1}(s)) - H(V_{\ell_1}(s))]}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\

@@

&= \frac{q * P_{T_1}(V_{\ell_1}(s)) \left[\log_2 q + \log_2 \left[\frac{P_{T_1}(V_{\ell_1}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right]  -H(V_{\ell_1}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}

@@

&= \frac{(1-q) * P_{T_2}(V_{\ell_2}(s)) \left[\log_2 (1-q) + \log_2 \left[\frac{P_{T_2}(V_{\ell_2}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] - H(V_{\ell_2}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}

@@

&= \frac{q * P_{T_1}(V_{\ell_1}(s)) \left[\log_2 q + \log_2 \left[\frac{P_{T_1}(V_{\ell_1}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] - H(V_{\ell_1}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\\
&+ \frac{(1-q) * P_{T_2}(V_{\ell_2}(s)) \left[\log_2 (1-q) + \log_2 \left[\frac{P_{T_2}(V_{\ell_2}(s))}{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}\right] - H(V_{\ell_2}(s)) \right] }{P(V_{ \MergeLOf{\Lens_1}{\Lens_2}}(s))}
